Surface programmable materials

### 2024-08-23 live.main.tex
modify main picture

\usepackage{svg}
\usepackage{amsmath}
\usepackage{graphicx}% Include figure files
\usepackage{textcomp}
\usepackage{bm}% bold math
\usepackage{color}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage{mathrsfs}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{txfonts}
\usepackage{algorithm}  
\usepackage{algpseudocode}  
\usepackage{balance}
\usepackage{flushend}
\usepackage{cleveref}
\usepackage{tikz}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}  % Use Input in the format of Algorithm  
\renewcommand{\algorithmicensure}{\textbf{Output:}} % Use Output in the format of Algorithm

@@

\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

\begin{center}
\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300

%Shape: Square [id:dp3257799447745866] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (30,30) -- (40,30) -- (40,54) -- (30,54) -- cycle ;
%Straight Lines [id:da8913459345633652] 
\draw    (20,42) -- (30,42) ;
%Straight Lines [id:da9790784501640646] 
\draw    (40,42) -- (60,42) ;
%Shape: Square [id:dp5326406990508012] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (70,30) -- (80,30) -- (80,54) -- (70,54) -- cycle ;
%Straight Lines [id:da008320062158621688] 
\draw    (80,42) -- (100,42) ;
%Shape: Square [id:dp29003962631292124] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (30,60) -- (40,60) -- (40,84) -- (30,84) -- cycle ;
%Straight Lines [id:da8695035786947396] 
\draw    (20,72) -- (30,72) ;
%Straight Lines [id:da417768427429108] 
\draw    (40,72) -- (60,72) ;
%Shape: Square [id:dp08018354727485644] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (70,60) -- (80,60) -- (80,84) -- (70,84) -- cycle ;
%Straight Lines [id:da7038299022670145] 
\draw    (80,72) -- (100,72) ;
%Shape: Square [id:dp4665291997770109] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (30,90) -- (40,90) -- (40,114) -- (30,114) -- cycle ;
%Straight Lines [id:da9280920191618629] 
\draw    (20,102) -- (30,102) ;
%Straight Lines [id:da023978392575592755] 
\draw    (40,102) -- (60,102) ;
%Shape: Square [id:dp9172017959293151] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (70,90) -- (80,90) -- (80,114) -- (70,114) -- cycle ;
%Straight Lines [id:da515300595667447] 
\draw    (80,102) -- (100,102) ;
%Straight Lines [id:da9288304396586808] 
\draw    (80,72) -- (100,72) ;
%Straight Lines [id:da852280866297966] 
\draw    (80,102) -- (100,102) ;
%Shape: Square [id:dp32738689596333903] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (30,160) -- (40,160) -- (40,184) -- (30,184) -- cycle ;
%Straight Lines [id:da07485978922844372] 
\draw    (20,172) -- (30,172) ;
%Straight Lines [id:da2475700164417307] 
\draw    (40,172) -- (60,172) ;
%Shape: Square [id:dp4553302503149699] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (70,160) -- (80,160) -- (80,184) -- (70,184) -- cycle ;
%Straight Lines [id:da5669313532997795] 
\draw    (80,172) -- (100,172) ;
%Shape: Square [id:dp681519742049937] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (163,30) -- (173,30) -- (173,54) -- (163,54) -- cycle ;
%Shape: Square [id:dp2901897648605303] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (163,60) -- (173,60) -- (173,84) -- (163,84) -- cycle ;
%Shape: Square [id:dp9710219091133365] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (163,90) -- (173,90) -- (173,114) -- (163,114) -- cycle ;
%Shape: Square [id:dp47295881968788644] 
\draw  [fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (163,160) -- (173,160) -- (173,184) -- (163,184) -- cycle ;
%Straight Lines [id:da1585638759400958] 
\draw    (173,172) -- (183,172) ;
%Straight Lines [id:da5795532995572801] 
\draw    (173,102) -- (183,102) ;
%Straight Lines [id:da8448651727682703] 
\draw    (173,72) -- (183,72) ;
%Straight Lines [id:da9060816552835422] 
\draw    (173,42) -- (183,42) ;
%Shape: Circle [id:dp818609500871543] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (42,42) .. controls (42,40.34) and (43.34,39) .. (45,39) .. controls (46.66,39) and (48,40.34) .. (48,42) .. controls (48,43.66) and (46.66,45) .. (45,45) .. controls (43.34,45) and (42,43.66) .. (42,42) -- cycle ;
%Shape: Circle [id:dp13831345755639668] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (42,72) .. controls (42,70.34) and (43.34,69) .. (45,69) .. controls (46.66,69) and (48,70.34) .. (48,72) .. controls (48,73.66) and (46.66,75) .. (45,75) .. controls (43.34,75) and (42,73.66) .. (42,72) -- cycle ;
%Shape: Circle [id:dp9041445092942773] 
\draw   (42,102) .. controls (42,100.34) and (43.34,99) .. (45,99) .. controls (46.66,99) and (48,100.34) .. (48,102) .. controls (48,103.66) and (46.66,105) .. (45,105) .. controls (43.34,105) and (42,103.66) .. (42,102) -- cycle ;
%Shape: Circle [id:dp7529245942690144] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (42,172) .. controls (42,170.34) and (43.34,169) .. (45,169) .. controls (46.66,169) and (48,170.34) .. (48,172) .. controls (48,173.66) and (46.66,175) .. (45,175) .. controls (43.34,175) and (42,173.66) .. (42,172) -- cycle ;
%Shape: Circle [id:dp4421700288524639] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (82,172) .. controls (82,170.34) and (83.34,169) .. (85,169) .. controls (86.66,169) and (88,170.34) .. (88,172) .. controls (88,173.66) and (86.66,175) .. (85,175) .. controls (83.34,175) and (82,173.66) .. (82,172) -- cycle ;
%Shape: Circle [id:dp4431783957619826] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (82,102) .. controls (82,100.34) and (83.34,99) .. (85,99) .. controls (86.66,99) and (88,100.34) .. (88,102) .. controls (88,103.66) and (86.66,105) .. (85,105) .. controls (83.34,105) and (82,103.66) .. (82,102) -- cycle ;
%Shape: Circle [id:dp403539897070186] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (42,102) .. controls (42,100.34) and (43.34,99) .. (45,99) .. controls (46.66,99) and (48,100.34) .. (48,102) .. controls (48,103.66) and (46.66,105) .. (45,105) .. controls (43.34,105) and (42,103.66) .. (42,102) -- cycle ;
%Shape: Circle [id:dp8783887479009327] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (82,72) .. controls (82,70.34) and (83.34,69) .. (85,69) .. controls (86.66,69) and (88,70.34) .. (88,72) .. controls (88,73.66) and (86.66,75) .. (85,75) .. controls (83.34,75) and (82,73.66) .. (82,72) -- cycle ;
%Shape: Circle [id:dp6224124506773947] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (82,42) .. controls (82,40.34) and (83.34,39) .. (85,39) .. controls (86.66,39) and (88,40.34) .. (88,42) .. controls (88,43.66) and (86.66,45) .. (85,45) .. controls (83.34,45) and (82,43.66) .. (82,42) -- cycle ;
%Shape: Circle [id:dp8043981259851258] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (175,102) .. controls (175,100.34) and (176.34,99) .. (178,99) .. controls (179.66,99) and (181,100.34) .. (181,102) .. controls (181,103.66) and (179.66,105) .. (178,105) .. controls (176.34,105) and (175,103.66) .. (175,102) -- cycle ;
%Shape: Circle [id:dp43816466417546707] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (175,172) .. controls (175,170.34) and (176.34,169) .. (178,169) .. controls (179.66,169) and (181,170.34) .. (181,172) .. controls (181,173.66) and (179.66,175) .. (178,175) .. controls (176.34,175) and (175,173.66) .. (175,172) -- cycle ;
%Shape: Circle [id:dp5620143122025991] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (175,72) .. controls (175,70.34) and (176.34,69) .. (178,69) .. controls (179.66,69) and (181,70.34) .. (181,72) .. controls (181,73.66) and (179.66,75) .. (178,75) .. controls (176.34,75) and (175,73.66) .. (175,72) -- cycle ;
%Shape: Circle [id:dp8865997979090963] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (175,42) .. controls (175,40.34) and (176.34,39) .. (178,39) .. controls (179.66,39) and (181,40.34) .. (181,42) .. controls (181,43.66) and (179.66,45) .. (178,45) .. controls (176.34,45) and (175,43.66) .. (175,42) -- cycle ;
%Shape: Circle [id:dp18306264726647137] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (42,202) .. controls (42,200.34) and (43.34,199) .. (45,199) .. controls (46.66,199) and (48,200.34) .. (48,202) .. controls (48,203.66) and (46.66,205) .. (45,205) .. controls (43.34,205) and (42,203.66) .. (42,202) -- cycle ;
%Shape: Circle [id:dp3243993178712161] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (42,12) .. controls (42,10.34) and (43.34,9) .. (45,9) .. controls (46.66,9) and (48,10.34) .. (48,12) .. controls (48,13.66) and (46.66,15) .. (45,15) .. controls (43.34,15) and (42,13.66) .. (42,12) -- cycle ;
%Shape: Circle [id:dp3529141461836287] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (135,12) .. controls (135,10.34) and (136.34,9) .. (138,9) .. controls (139.66,9) and (141,10.34) .. (141,12) .. controls (141,13.66) and (139.66,15) .. (138,15) .. controls (136.34,15) and (135,13.66) .. (135,12) -- cycle ;
%Shape: Circle [id:dp9431375452836528] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (135,202) .. controls (135,200.34) and (136.34,199) .. (138,199) .. controls (139.66,199) and (141,200.34) .. (141,202) .. controls (141,203.66) and (139.66,205) .. (138,205) .. controls (136.34,205) and (135,203.66) .. (135,202) -- cycle ;
%Straight Lines [id:da9696356596865732] 
\draw    (5,42) -- (20,42) ;
%Straight Lines [id:da5317592058087168] 
\draw    (5,72) -- (20,72) ;
%Straight Lines [id:da6169293205402535] 
\draw    (5,102) -- (20,102) ;
%Straight Lines [id:da9653690034485647] 
\draw    (5,172) -- (20,172) ;
%Shape: Circle [id:dp11541023046031418] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (2,42) .. controls (2,40.34) and (3.34,39) .. (5,39) .. controls (6.66,39) and (8,40.34) .. (8,42) .. controls (8,43.66) and (6.66,45) .. (5,45) .. controls (3.34,45) and (2,43.66) .. (2,42) -- cycle ;
%Shape: Circle [id:dp9967907554667488] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (2,72) .. controls (2,70.34) and (3.34,69) .. (5,69) .. controls (6.66,69) and (8,70.34) .. (8,72) .. controls (8,73.66) and (6.66,75) .. (5,75) .. controls (3.34,75) and (2,73.66) .. (2,72) -- cycle ;
%Shape: Circle [id:dp5466737045582317] 
\draw   (2,102) .. controls (2,100.34) and (3.34,99) .. (5,99) .. controls (6.66,99) and (8,100.34) .. (8,102) .. controls (8,103.66) and (6.66,105) .. (5,105) .. controls (3.34,105) and (2,103.66) .. (2,102) -- cycle ;
%Shape: Circle [id:dp22351697734701603] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (2,172) .. controls (2,170.34) and (3.34,169) .. (5,169) .. controls (6.66,169) and (8,170.34) .. (8,172) .. controls (8,173.66) and (6.66,175) .. (5,175) .. controls (3.34,175) and (2,173.66) .. (2,172) -- cycle ;
%Shape: Circle [id:dp07423205757027329] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (2,102) .. controls (2,100.34) and (3.34,99) .. (5,99) .. controls (6.66,99) and (8,100.34) .. (8,102) .. controls (8,103.66) and (6.66,105) .. (5,105) .. controls (3.34,105) and (2,103.66) .. (2,102) -- cycle ;
%Shape: Circle [id:dp44591669371444054] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (2,202) .. controls (2,200.34) and (3.34,199) .. (5,199) .. controls (6.66,199) and (8,200.34) .. (8,202) .. controls (8,203.66) and (6.66,205) .. (5,205) .. controls (3.34,205) and (2,203.66) .. (2,202) -- cycle ;
%Shape: Circle [id:dp8124810079347506] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (2,12) .. controls (2,10.34) and (3.34,9) .. (5,9) .. controls (6.66,9) and (8,10.34) .. (8,12) .. controls (8,13.66) and (6.66,15) .. (5,15) .. controls (3.34,15) and (2,13.66) .. (2,12) -- cycle ;
%Curve Lines [id:da6837659640523519] 
\draw    (12,72) .. controls (11.9,72.82) and (16.25,48.02) .. (30,48) ;
%Curve Lines [id:da14157714470554095] 
\draw    (12,102) .. controls (12.25,102.02) and (16.25,78.02) .. (30,78) ;
%Curve Lines [id:da29397752720095016] 
\draw    (10,132) .. controls (9.9,131.92) and (16.25,108.02) .. (30,108) ;
%Curve Lines [id:da1010168964172955] 
\draw    (8,202) .. controls (7.88,201.94) and (16.25,178.02) .. (30,178) ;
%Curve Lines [id:da41907939317602727] 
\draw    (30,66) .. controls (15.95,66.07) and (11.95,42.82) .. (12,42) ;
%Curve Lines [id:da4960426207730133] 
\draw    (30,96) .. controls (15.95,96.07) and (11.95,72.82) .. (12,72) ;
%Curve Lines [id:da32194834856252696] 
\draw    (30,126) .. controls (15.95,126.07) and (11.95,102.82) .. (12,102) ;
%Curve Lines [id:da9942559529163806] 
\draw    (30,166) .. controls (15.95,166.07) and (9.95,142.82) .. (10,142) ;
%Curve Lines [id:da30812169087400987] 
\draw    (30,36) .. controls (15.95,36.07) and (7.95,12.82) .. (8,12) ;
%Curve Lines [id:da7415436207281032] 
\draw    (12,172) .. controls (12.4,171.42) and (16.25,148.02) .. (30,148) ;
%Straight Lines [id:da945225908298071] 
\draw    (59.5,42) -- (69.5,42) ;
%Straight Lines [id:da019486859954932045] 
\draw    (59.5,72) -- (69.5,72) ;
%Straight Lines [id:da10691701544026788] 
\draw    (59.5,102) -- (69.5,102) ;
%Straight Lines [id:da08190608552147682] 
\draw    (59.5,172) -- (69.5,172) ;
%Straight Lines [id:da5383715063718815] 
\draw    (48,42) -- (59.5,42) ;
%Straight Lines [id:da29185686612996165] 
\draw    (48,72) -- (59.5,72) ;
%Straight Lines [id:da6312076314118666] 
\draw    (48,102) -- (59.5,102) ;
%Straight Lines [id:da0122276432828059] 
\draw    (48,172) -- (59.5,172) ;
%Curve Lines [id:da634843349549117] 
\draw    (51.5,72) .. controls (51.4,72.82) and (55.75,48.02) .. (69.5,48) ;
%Curve Lines [id:da29334484540724026] 
\draw    (51.5,102) .. controls (51.75,102.02) and (55.75,78.02) .. (69.5,78) ;
%Curve Lines [id:da3089090169112314] 
\draw    (49.5,132) .. controls (49.4,131.92) and (55.75,108.02) .. (69.5,108) ;
%Curve Lines [id:da24605443838188257] 
\draw    (47.5,202) .. controls (47.38,201.94) and (55.75,178.02) .. (69.5,178) ;
%Curve Lines [id:da497728473744927] 
\draw    (69.5,66) .. controls (55.45,66.07) and (51.45,42.82) .. (51.5,42) ;
%Curve Lines [id:da1733603989545598] 
\draw    (69.5,96) .. controls (55.45,96.07) and (51.45,72.82) .. (51.5,72) ;
%Curve Lines [id:da7391016400644088] 
\draw    (69.5,126) .. controls (55.45,126.07) and (51.45,102.82) .. (51.5,102) ;
%Curve Lines [id:da2610882313501728] 
\draw    (69.5,166) .. controls (55.45,166.07) and (49.45,142.82) .. (49.5,142) ;
%Curve Lines [id:da9723708662465751] 
\draw    (69.5,36) .. controls (55.45,36.07) and (47.45,12.82) .. (47.5,12) ;
%Curve Lines [id:da7225849641270694] 
\draw    (51.5,172) .. controls (51.9,171.42) and (55.75,148.02) .. (69.5,148) ;
%Straight Lines [id:da7791377752665631] 
\draw    (100,42) -- (110,42) ;
%Straight Lines [id:da23522073116206266] 
\draw    (100,72) -- (110,72) ;
%Straight Lines [id:da18218908732788264] 
\draw    (100,102) -- (110,102) ;
%Straight Lines [id:da3309320538017131] 
\draw    (100,172) -- (110,172) ;
%Straight Lines [id:da4610992726495633] 
\draw    (88,42) -- (100,42) ;
%Straight Lines [id:da1358122827839865] 
\draw    (88,72) -- (100,72) ;
%Straight Lines [id:da9749891373044985] 
\draw    (88,102) -- (100,102) ;
%Straight Lines [id:da6902822758606824] 
\draw    (88,172) -- (100,172) ;
%Curve Lines [id:da8937700604447827] 
\draw    (92,72) .. controls (91.9,72.82) and (96.25,48.02) .. (110,48) ;
%Curve Lines [id:da3731849249187291] 
\draw    (92,102) .. controls (92.25,102.02) and (96.25,78.02) .. (110,78) ;
%Curve Lines [id:da9742316406042617] 
\draw    (88,202) .. controls (87.88,201.94) and (96.25,178.02) .. (110,178) ;
%Curve Lines [id:da6734623491912421] 
\draw    (110,66) .. controls (95.95,66.07) and (91.95,42.82) .. (92,42) ;
%Curve Lines [id:da9728942718366658] 
\draw    (110,96) .. controls (95.95,96.07) and (91.95,72.82) .. (92,72) ;
%Curve Lines [id:da5314963895208473] 
\draw    (110,126) .. controls (95.95,126.07) and (91.95,102.82) .. (92,102) ;
%Curve Lines [id:da20527729986926668] 
\draw    (110,36) .. controls (95.95,36.07) and (87.95,12.82) .. (88,12) ;
%Curve Lines [id:da9357477032373158] 
\draw    (92,172) .. controls (92.4,171.42) and (96.25,148.02) .. (110,148) ;
%Shape: Circle [id:dp03524070526370693] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (82,12) .. controls (82,10.34) and (83.34,9) .. (85,9) .. controls (86.66,9) and (88,10.34) .. (88,12) .. controls (88,13.66) and (86.66,15) .. (85,15) .. controls (83.34,15) and (82,13.66) .. (82,12) -- cycle ;
%Shape: Circle [id:dp5282167504002355] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (82,202) .. controls (82,200.34) and (83.34,199) .. (85,199) .. controls (86.66,199) and (88,200.34) .. (88,202) .. controls (88,203.66) and (86.66,205) .. (85,205) .. controls (83.34,205) and (82,203.66) .. (82,202) -- cycle ;
%Straight Lines [id:da28818147273527717] 
\draw    (133.6,41.96) -- (153.6,41.96) ;
%Straight Lines [id:da4792679687432131] 
\draw    (133.6,71.96) -- (153.6,71.96) ;
%Straight Lines [id:da2794298478395634] 
\draw    (133.6,101.96) -- (153.6,101.96) ;
%Straight Lines [id:da610925391950311] 
\draw    (133.6,171.96) -- (153.6,171.96) ;
%Straight Lines [id:da31436080279800227] 
\draw    (153.1,41.96) -- (163.1,41.96) ;
%Straight Lines [id:da07642255702447143] 
\draw    (153.1,71.96) -- (163.1,71.96) ;
%Straight Lines [id:da48431709040149795] 
\draw    (153.1,101.96) -- (163.1,101.96) ;
%Straight Lines [id:da31077160308421736] 
\draw    (153.1,171.96) -- (163.1,171.96) ;
%Straight Lines [id:da4482666583263508] 
\draw    (141.6,41.96) -- (153.1,41.96) ;
%Straight Lines [id:da0031324911441572567] 
\draw    (141.6,71.96) -- (153.1,71.96) ;
%Straight Lines [id:da39186514465416056] 
\draw    (141.6,101.96) -- (153.1,101.96) ;
%Straight Lines [id:da9984443909601395] 
\draw    (141.6,171.96) -- (153.1,171.96) ;
%Curve Lines [id:da2794596982451869] 
\draw    (145.1,71.96) .. controls (145,72.79) and (149.35,47.99) .. (163.1,47.96) ;
%Curve Lines [id:da5527279625811088] 
\draw    (145.1,101.96) .. controls (145.35,101.99) and (149.35,77.99) .. (163.1,77.96) ;
%Curve Lines [id:da49469050221037403] 
\draw    (143.1,131.96) .. controls (143,131.89) and (149.35,107.99) .. (163.1,107.96) ;
%Curve Lines [id:da5889227861048327] 
\draw    (141.1,201.96) .. controls (140.98,201.9) and (149.35,177.99) .. (163.1,177.96) ;
%Curve Lines [id:da046574817758556986] 
\draw    (163.1,65.96) .. controls (149.05,66.04) and (145.05,42.79) .. (145.1,41.96) ;
%Curve Lines [id:da2878436840249363] 
\draw    (163.1,95.96) .. controls (149.05,96.04) and (145.05,72.79) .. (145.1,71.96) ;
%Curve Lines [id:da49553051429298844] 
\draw    (163.1,125.96) .. controls (149.05,126.04) and (145.05,102.79) .. (145.1,101.96) ;
%Curve Lines [id:da6292297348811737] 
\draw    (163.1,165.96) .. controls (149.05,166.04) and (143.05,142.79) .. (143.1,141.96) ;
%Curve Lines [id:da8001909344877356] 
\draw    (163.1,35.96) .. controls (149.05,36.04) and (141.05,12.79) .. (141.1,11.96) ;
%Curve Lines [id:da549670443628927] 
\draw    (145.1,171.96) .. controls (145.5,171.39) and (149.35,147.99) .. (163.1,147.96) ;
%Shape: Circle [id:dp3208676418353624] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (135,42) .. controls (135,40.34) and (136.34,39) .. (138,39) .. controls (139.66,39) and (141,40.34) .. (141,42) .. controls (141,43.66) and (139.66,45) .. (138,45) .. controls (136.34,45) and (135,43.66) .. (135,42) -- cycle ;
%Shape: Circle [id:dp3190617032943761] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (135,72) .. controls (135,70.34) and (136.34,69) .. (138,69) .. controls (139.66,69) and (141,70.34) .. (141,72) .. controls (141,73.66) and (139.66,75) .. (138,75) .. controls (136.34,75) and (135,73.66) .. (135,72) -- cycle ;
%Shape: Circle [id:dp5981517901086082] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (135,102) .. controls (135,100.34) and (136.34,99) .. (138,99) .. controls (139.66,99) and (141,100.34) .. (141,102) .. controls (141,103.66) and (139.66,105) .. (138,105) .. controls (136.34,105) and (135,103.66) .. (135,102) -- cycle ;
%Shape: Circle [id:dp9782081274652843] 
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (135,172) .. controls (135,170.34) and (136.34,169) .. (138,169) .. controls (139.66,169) and (141,170.34) .. (141,172) .. controls (141,173.66) and (139.66,175) .. (138,175) .. controls (136.34,175) and (135,173.66) .. (135,172) -- cycle ;

% Text Node
\draw (108,33) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
% Text Node
\draw (108,63) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
% Text Node
\draw (108,93.29) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
% Text Node
\draw (108,163) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
% Text Node
\draw (160,127.17) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
% Text Node
\draw (17,127.17) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
% Text Node
\draw (56.5,127.17) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
% Text Node
\draw (97,127.17) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
% Text Node
\draw (150.1,127.13) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};

\end{tikzpicture}
\end{center}

@@

\subsection{Cooling computation with direction}\label{sec:direction}

@@

The process of heating and annealing the entire material does not have computational capability, as the system lacks logical directionality.

Logical directionality needs to be introduced through an orderly annealing method. 
Similar to the localized heating-annealing approach that catalyzes the growth of ordered crystals, we introduced a temperature gradient annealing scheme.

More specifically, the computation, with computing direction from in-surface to out-surface, contains the following steps: (1). Initialize the in-surface configuration. By removing
some atoms on the in-surface. (2). Connect the in-surface/out-surface to
external heat sources at temperature $T_1 < T_2$, respectively. We
also require that the energy gap between the ground state and the first
excited state of the Hamiltonian to be $\Delta E< T_1$. (3). Lower the
temperature of the heat sources ``slowly'' to cool the system to the
ground state of the Hamiltonian. The temperature of the heat sources at
time $t$ is $T_{1/2}(t) = T_{1/2}(0)\lambda^{-c t}$, where
$T_{1/2}(0)$ is the initial temperature of the heat sources, and
$\alpha$ is a constant.

The computing direction could be reversed by swaping the temperature of the heat sources connected in-surface and out-surface.
However, solving the ground state from the non-deterministic direction is at least as hard as solving the circuit satisfiability problem, which is NP-complete~\cite{Moore2011}.

@@

\subsubsection{Estimation of the computing time along computation direction}\label{estimation-of-the-computing-time}

We fixed the width of each layer and denote $m$ as the number of layers in this material.

Let the temperature of the $k$-th layer at time $t$ be
$T(t, k) = T \lambda^{ct - k}$, where $T$ is the initial
temperature, $c$ is a constant, and $\lambda < 1$ is a constant. At
any given time $t$, we denote the subset of atoms at depth
$ct-\frac{W}{2}\le k \le ct + \frac{W}{2}$ as the \textbf{active zone},
where $W$ is the width of the sliding window such that
$e^{-\Delta E_{max} /\lambda^{W/2}} = \epsilon \ll 1$. The active zone
is the region where non-trivial computation occurs. The atoms outside
the active zone are either frozen or completely randomized.

Clearly, $W$ asymptotically scales as $\frac{\log(-\frac{1}{\log{\epsilon}})}{\log(\lambda)}$. The situations we care about
are those $\lambda \lessapprox 1$, so one can rewrite $W$ as $W \approx (1-\lambda)^{-1} \log(-\frac{1}{\log\epsilon})$.

We consider thermalizing the system in units of $W$. $\epsilon$ is
the error probability of each unit of time, which should scale as
$\epsilon \sim\left(\frac{m}{W}\right)^{-1}$.

>>>>

\usepackage{svg}
\usepackage{amsmath}
\usepackage{graphicx}% Include figure files
\usepackage{textcomp}
\usepackage{bm}% bold math
\usepackage{color}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage{mathrsfs}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{txfonts}
\usepackage{algorithm}  
\usepackage{algpseudocode}  
\usepackage{balance}
\usepackage{flushend}
\usepackage{cleveref}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}  % Use Input in the format of Algorithm  
\renewcommand{\algorithmicensure}{\textbf{Output:}} % Use Output in the format of Algorithm

\usepackage{svg}
\usepackage{amsmath}
\usepackage{graphicx}% Include figure files
\usepackage{textcomp}
\usepackage{bm}% bold math
\usepackage{color}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage{mathrsfs}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{txfonts}
\usepackage{algorithm}  
\usepackage{algpseudocode}  
\usepackage{balance}
\usepackage{flushend}
\usepackage{cleveref}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}  % Use Input in the format of Algorithm  
\renewcommand{\algorithmicensure}{\textbf{Output:}} % Use Output in the format of Algorithm

@@

@@

\subsection{C}\label{sec:direction}

@@

The computation contains the following steps: (1). Initialize the in-surface configuration. By removing
some atoms on the in-surface. (2). Connect the in-surface/out-surface to
external heat sources at temperature $T_1 < T_2$, respectively. We
also require that the energy gap between the ground state and the first
excited state of the Hamiltonian to be $\Delta E< T_1$. (3). Lower the
temperature of the heat sources ``slowly'' to cool the system to the
ground state of the Hamiltonian. The temperature of the heat sources at
time $t$ is $T_{1/2}(t) = T_{1/2}(0)\lambda^{-c t}$, where
$T_{1/2}(0)$ is the initial temperature of the heat sources, and
$\alpha$ is a constant.

Solving the ground state of the Hamiltonian of the Surface Programmable Material from the non-deterministic direction is at least as hard as solving the circuit satisfiability problem, which is NP-complete~\cite{Moore2011}.

@@

\subsubsection{Local cooling test through simulated
annealing}\label{local-cooling-test-through-simulated-annealing}

We will refer to a toy-model limit: $\Delta = 1$ and $U = \infty$.
What's more, we introduced \textbf{``Energy Gradient''} to the gadget to
provide directionality for the simulated annealing. The hamiltonian for
a m-layers automaton now change the form into:

\[
H = \sum_{|\vec r_i - \vec r_j|\leq 2} U \hat n_i \hat n_j  - \Delta \sum_{i,k|\text{vertice i belongs to layer k}} w_i \lambda^{m-k} \hat n_i
\]

The last term of our new hamiltonian represent the \textbf{``Energy
Gradient''}. For vertice $i$ in the k-th layer along the computation
direction, we reset its weight to $w_i\lambda^{m-k}$.

From an intuitive perspective, for layers where the thermal energy
exceeds the energy required to flip the nodes in the current layer,
simulated annealing always filps them randomly; for layers where the
thermal energy is lower than the energy required to flip the nodes in
the current layer, simulated annealing tends to maintain their
configuration; for layers where the thermal energy is just comparable to
the flipping energy, simulated annealing executes the corresponding
cooling process.

Hence, we can simply set the discrete annealing tempretures as
$T(k) = T_0 \eta^k$, where $\eta < 1$ and $\eta ^R = \lambda$.
Here $R$ represent the number of the cooling iterations performed for
a given layer.

Similar to what we did in QAA, firstly, we set the weights of the
inputs/outputs vertices to $\infty$ (NOTE: by removing vertices) for
testing doing computation along deterministic
direction/non-deterministic direction. Then we compare the probability
of successfully finding the corresponding ground state under certain
$T_0, R, \lambda$ and $\eta$. \textbf{We find that doing computation
along the non-deterministic direction is harder than the other one}

Next, we believe that for each layers's cooling process, we are
essentially calculating a probability transition matrix $P(T,k)$,
where $P(T,k)_{outputm, inputm}$ represent the probability that, given
the input vertices state is $inputm$, the cooling process sets the
output vertices state to $outputm$.
